Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-17 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added figures/BridgeMoreBuilding.pdf
basically finished section of methodology

Notice that after growing the additional bridges may be too close to buildings 
from another group.
We iteratively aggregate buildings.
This time we grow the original buildings with bridges.
Similar to what we do before, we aggregate buildings by introducing bridges.
We stop this iteration until the number of group does not decrease anymore.

@@

\subsection{Generating the goal forms of buildings}
\label{sec:Goal}
To generate the goal forms of buildings, we set time $t=1$.
We group (see \sect\ref{sec:Group}) 
and merge (see \sect\ref{sec:Aggregate}) buildings on start map.
Then we grow (see \sect\ref{sec:Grow}) 
and simplify (see \sect\ref{sec:DilationErosion}) the merged buildings.
See for example \fig\ref{fig:Buffer_MiterLimits}, 
the building at time $t=1$ is the goal form of the three buildings of $t=0$.

@@

A building on an intermediate map should never exceed
the goal form of the group of buildings 
which include the united buildings. 
Otherwise, the building will need to be shrunk.
To guarantee the non-exceeding, 
we clip the building by the goal form 
and remove the parts outside.
\todo{example?}

>>>>

Aggregated buildings may become too close after growing because of bridges.
\fig\ref{fig:BridgeMoreBuilding} shows such an example.
We grow and buffer buildings $p$, $q$, and~$r$.
As the buffers of $q$ and~$r$ overlap with each other
(see \fig\ref{fig:BridgeMoreBuilding}c),
we aggregated buildings $q$ and~$r$ by adding a bridge.
There are two buildings left in \fig\ref{fig:BridgeMoreBuilding}d.
Because of the bridge, when we grow and buffer the buildings in 
\fig\ref{fig:BridgeMoreBuilding}d, 
the buffer of building $p$ overlap with the buffer of the bridged $q$ and $r$
(see \fig\ref{fig:BridgeMoreBuilding}f).
We aggregate building $p$ with bridged $q$ and $r$
(see \fig\ref{fig:BridgeMoreBuilding}g).
There is one building left in \fig\ref{fig:BridgeMoreBuilding}g.
Then we grow and buffer again.
There is one building left after this process.
The number of buildings does not decrease comparing to last process.
The iteration stops.

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{BridgeMoreBuilding}
	\caption{Iteratively aggregating close buildings by adding bridges.
		(a) original buildings $p$, $q$, and~$r$.
		(b) grow the original buildings with distance $\dtrm{G}$.
		(c) buffer the grown buildings with distance $d_{\epsilon,t}/2$ using 
		round joins.
		(d) aggregate buildings $q$ and~$r$ by adding a bridge,
		as their buffer overlap with each other in (c).
		(e) grow the buildings in (d) with distance $\dtrm{G}$.
		(f) buffer the grown buildings in (e) with distance $d_{\epsilon,t}/2$ 
		using round joins.
		(g) aggregate buildings $p$, $q$ and~$r$ by adding bridges.
		(h) grow the buildings in (g) with distance $\dtrm{G}$.
		(i) buffer the grown buildings in (h) with distance $d_{\epsilon,t}/2$ 
		using round joins.
	}
	\label{fig:BridgeMoreBuilding}
\end{figure}

@@

\subsection{Generating the goal forms of buildings}
\label{sec:Goal}
To generate the goal forms of buildings, we set time $t=1$.
We aggregate original buildings (see \sect\ref{sec:Aggregate}).
Then we grow (see \sect\ref{sec:Grow}) 
and simplify 
(see \sects\ref{sec:DilationErosion} and~\ref{sec:ImaiIri}) the grown buildings.
See for example \fig\ref{fig:GrowAndBridge}, 
the building at time $t=1$ is the goal form of the three original buildings of.

@@

A building on an intermediate map should never exceed
the goal form of the group of buildings 
which include the united buildings. 
Otherwise, the building will need to be shrunk.
To guarantee the non-exceeding, 
we clip the building using the goal form 
and remove the parts outside.
